---
title: "2. The Whole Game.rmd"
author: "Russ Conte"
date: "2022-12-12"
output: html_document
---

## 2.1 Introduction

This chapter runs through the development of a small toy package. It’s meant to paint the Big Picture and suggest a workflow, before we descend into the detailed treatment of the key components of an R package.

## 2.2 Load devtools and friends

Load the `devtools` package, which is the public face of a set of packages that support various aspects of package development. The most obvious of these is the `usethis` package, which you’ll see is also being loaded.

```{r Load the devtools package}

library(devtools)

```

Check the version of devtools that is on my computer, see if it's the same as the author's version:

```{r Check version of devtools on my computer}

packageVersion("devtools")

```

I'm using devtools version 2.4.5, and that's the same as the author's version.

## 2.3 Toy package: regexcite

We use various functions from devtools to build a small toy package from scratch, with features commonly seen in released packages:

-   Functions to address a specific need, in this case helpers for work with regular expressions.<br>
        - Version control and an open development process.<br>
        - This is completely optional in your work, but highly recommended. You’ll see how Git and GitHub help us expose all the intermediate stages of our toy package.<br>
-   Access to established workflows for installation, getting help, and checking quality.<br>
    - Documentation for individual functions via roxygen2.<br>
    - Unit testing with testthat.<br>
Documentation for the package as a whole via an executable README.Rmd.