---
title: "2. The Whole Game.RMD"
author: "Russ Conte"
date: "2022-12-12"
output: html_document
---

## 2.1 Introduction

This chapter runs through the development of a small toy project. It’s meant to paint the Big Picture and suggest a workflow, before we descend into the detailed treatment of the key components of an R package.

## 2.2 Load devtools and friends

Load the devtools package, which is the public face of a set of packages that support various aspects of package development. The most obvious of these is the usethis package, which you’ll see is also being loaded.

```{r Load devtools}

library(devtools)

```

```{r Check the version of devtools}

packageVersion("devtools")

```

The verison of devtools on my computer matches the one the authors are using, 2.4.5.

## 2.3 Toy package: regexcite

We use various functions from devtools to build a small toy package from scratch, with features commonly seen in released packages:

• Functions to address a specific need, in this case helpers for work with regular expressions.<br>
• Version control and an open development process.<br>
• This is completely optional in your work, but highly recommended. You’ll see how Git and GitHub help us expose all the intermediate stages of our toy package.<br>
• Access to established workflows for installation, getting help, and checking quality.<br>
• Documentation for individual functions via [roxygen2](https://cran.r-project.org/package=roxygen2).<br>
• Unit testing with [testthat](https://testthat.r-lib.org/).<br>
• Documentation for the package as a whole via an executable `README.Rmd`.<br>

## 2.4 Peek at the finished product

You can see the glorious result we are working towards by visiting regexcite on [GitHub](https://github.com/jennybc/regexcite)