---
title: "3. System Setup.rmd"
author: "Russ Conte"
date: "2022-12-13"
output: html_document
---
## 3.1 Prepare your system

To get started, make sure you have the latest version of R (at least 4.2.2, which is the version being used to render this book), then run the following code to get the packages you’ll need:

```{r}
install.packages(c("devtools", "roxygen2", "testthat", "knitr"))
```

Example of how to simulate installing and loading a package, during interactive development:

```{r}

library(devtools)
load_all()

```

## 3.2.1 Personal Configuration

Attach devtools as follows:

```{r}

library(devtools)
```

## 3.3 R build toolchain

To be fully capable of building R packages from source, you’ll also need a compiler and a few other command line tools. This may not be strictly necessary until you want to build packages containing C or C++ code. Especially if you are using RStudio, you can set this aside for now. The IDE will alert you and provide support once you try to do something that requires you to setup your development environment. Read on for advice on doing this yourself.

## 3.3.4 Verify system prep :) (an excellent idea!!)

You can request a “(package) development situation report” with `devtools::dev_sitrep()`:

```{r}

devtools::dev_sitrep()

```

Interesting response from R:

devtools or its dependencies out of date:
  'evaluate'
  Update them with `devtools::update_packages("devtools")`── dev package 
  
Therefore:

```{r}

devtools::update_packages("devtools")

```

Now repeat the package situation report, to test if the system is current:

```{r}

devtools::dev_sitrep()
```

All checks passed, good so far!!